Woman in Workplace ^[Code and data are available at:https://github.com/Faustine123/Newspapers-in-Times-of-Low-Advertising-Revenues]

### 2023-04-21 Output/Paper/Paper.qmd
discussion

## Discussion
### Woman Fortune 500 CEOs

### Limitations and Next steps

@@

Additional Details{-}

>>>>

## Discussion
### Woman Fortune 500 CEOs
The percentage of female CEOs in the Fortune 500 has been increasing over the years, but remains low, with only 4.8% of CEO positions being held by women by 2018. The slow growth in the percentage of female CEOs is evidence that women continue to face significant barriers to entry and advancement in the corporate world. Some of the barriers include gender bias, lack of access to networks, and limited development and training opportunities. In addition, societal bias and intolerance of women's marital and reproductive and physical status leads to greater difficulty in promoting women [@heilman2018gender]. Such societal expectations and stereotypes of gender roles may lead to underrepresentation of women in leadership positions, resulting in the disenfranchisement of women.

Studies have shown that having women in top leadership positions improves financial performance and corporate social responsibility[@boardroom]. Therefore, it is critical for companies to promote gender diversity in leadership positions. This can be achieved by implementing policies and initiatives that address the barriers faced by women, provide development and training opportunities, and foster an inclusive corporate culture that values diversity. The lack of representation of women in executive leadership positions is not only an ethical issue, but also an economic one, as research shows that companies with diverse leadership teams perform better financially. By promoting gender equality in leadership roles, companies can tap into a broader pool of talent, bring new perspectives and ideas to the table, and ultimately improve their bottom line. It is critical for companies to prioritize diversity and inclusion efforts and work to create a more fair and equitable workplace for everyone.

In conclusion, while progress has been made in increasing the percentage of female CEOs in the Fortune 500, it is clear that there is still a long way to go to achieve gender parity in top leadership positions. Companies must actively work to address the barriers women face and promote gender diversity in leadership to benefit from a diverse and inclusive workplace. Women need to break through societal biases and work to overcome the stereotypes of women themselves that have been planted in the minds of a patriarchal society.

### Woman University Presidents in US
The gender gap in higher education leadership positions in the United States has been the subject of growing concern. While our society has also made progress in recent decades in appointing women to university presidencies, there remains a significant gap between men and women in higher education leadership roles. Women continue to be underrepresented in top leadership positions, including college presidents, department chairs, and provosts. This disparity is even more pronounced in science, technology, engineering and mathematics (STEM) fields, where women are significantly underrepresented in leadership positions.

And it has been shown that female and male university presidents maintain similar overall leadership behaviors and attitudes, with differences in responses based on the administrators' years of higher education experience, not gender [@wheeler1989male]. This leads us to reflect on where such a social phenomenon actually originates. In male-dominated social structures, gender gaps in higher education leadership can be attributed to a variety of factors, including gender bias in hiring and promotion practices, and social and cultural barriers that limit women's access to these positions. There is also evidence of a lack of mentoring and sponsorship opportunities for women in academia, which may all be a result of our society's unconscious or conscious disparagement of women. Despite efforts to promote diversity and inclusion, these barriers exacerbate the persistent gender gap in higher education leadership.

To address this disparity, many universities and academic institutions have begun to implement policies and programs designed to promote diversity and inclusion in their hiring and promotion practices. Some universities have implemented affirmative action policies that require a certain percentage of leadership positions to be held by women, while others have developed programs to recruit and mentor women in leadership positions. In addition, some institutions have implemented unconscious bias training for faculty and staff to address implicit bias in hiring and promotion practices. It is important to continue to monitor and address the gender gap in higher education leadership to ensure that our institutions of higher education are truly representative of the diverse communities they serve. By promoting diversity and inclusion in leadership roles, universities and academic institutions can create a more inclusive environment that reflects the values of equity and opportunity for all.

### Hihg-Education Gender Comparison in US
The number of women completing higher education after 1992 has surpassed that of men, with women accounting for more than 54.32% of total higher education completers in 2021. In the overall society, women and men have equal or even better access to education, yet the percentage of female CEOs and female university presidents is pathetically low. With the advancement of social civilization, the status of women has gradually improved, and various policies and cultures of gender equality have gradually taken shape. Many women are complacent about this, yet even after completing higher education, women often face barriers to promotion and equal pay in their careers.

Even though companies have many gender equality rules and regulations, many HRs are always mindful of women's physiological periods, relationship status, and childbirth status when balancing the interests of the company, while ostensibly rejecting female applicants on other excuses. Moreover, in a patriarchal society, do you hear that women are just not as good at math as men? However, the truth is that people's performance in any field has nothing to do with gender. More and more women are now entering STEM fields of study.

Overall, despite the fact that women are becoming more educated, women continue to suffer from inequality in the workplace and in society. Promoting equal advancement opportunities and fair pay for women in their careers depends not only on the efforts of companies, but also on the stripping away of stereotypes in the minds of all in society.

### Gender Wage Gap in US
The gender wage gap has been a persistent problem in the United States. Despite all efforts to close the gap, there is still a huge disparity between the earnings of men and women in the workforce. A study conducted by the National Women's Law Center (NWLC) found that American female men earn 82 cents for every dollar earned, and the gap is even greater for women of color. This disparity not only affects individual women, but has a ripple effect on families, communities and the overall economy.

Efforts to close the gender wage gap have been ongoing, including the passage of the Equal Pay Act of 1963 and the Lilly Ledbetter Fair Pay Act of 2009. However, there is still much work to be done to ensure that women are paid fairly for their work. Employers can play a key role in addressing the wage gap by conducting pay equity analyses, eliminating bias in hiring and promotion decisions, and providing family-friendly policies such as paid family leave and flexible work arrangements. In addition, policymakers can implement measures such as raising the minimum wage, providing affordable child care, and enforcing equal pay laws. By addressing the root causes of the wage gap and promoting policies that support women in the workforce, we can create a more equitable and prosperous society for all.

Furthermore, in a society where women bear the burden of childbirth, while suffering demotions, blame, and other workplace bullying because of it. The bullying of women in society is reflected in the workplace. Gender equality requires the concerted efforts of all people, and there is a long way to go.

### Limitations and Next steps
A potential weakness of this paper is that the data used may not be comprehensive enough, in terms of year, amount of data, etc. In addition, the dataset only represents responses from the United States, which limits its generalizability to countries with different cultural backgrounds (e.g., Asian or South American countries). The selected dataset is only a portion of the factors that influence female workplace discrimination. In addition, due to a personal error, the datasets selected for this paper could not use the same model; they do not have the same two variables.

Therefore, the conclusions drawn in this paper may not accurately reflect the full range of factors that lead to workplace discrimination against women, and the findings may only reflect part of the phenomenon. It is important to keep in mind that the conclusions drawn in this paper are based on data from the United States only and may not be representative of the entire world. These findings should be applied with caution to other countries or regions, which requires you to read and apply the findings with critical thinking.

In the future, I will be looking to examine more of the primary factors that contribute to discrimination and bias against women in the workplace and in society. I am committed to eliminating these biases and discrimination.

@@

**Additional Details**
